%
% PROJECT: <ETD> Electronic Thesis and Dissertation Initiative
%   TITLE: LaTeX report template for ETDs in LaTeX
%  AUTHOR: Neill Kipp, nkipp@vt.edu
%     URL: http://etd.vt.edu/latex/
% SAVE AS: etd.tex
% REVISED: September 6, 1997 [GMc 8/30/10]
% 

% Instructions: Remove the data from this document and replace it with your own,
% keeping the style and formatting information intact.  More instructions
% appear on the Web site listed above.

\documentclass[12pt]{report}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1in}

% Uncomment for double-spaced document.
% \renewcommand{\baselinestretch}{2}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{ifthen}
\usepackage{standalone}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{subfig}
\usepackage{floatrow}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
% \usepackage{epsf}

\begin{document}

\thispagestyle{empty}
\pagenumbering{roman}
\begin{center}

% TITLE
{\Large 
Replication of Concurrent Applications in a Shared Memory Multikernel
}

\vfill

Yuzhong Wen

\vfill

Thesis submitted to the Faculty of the \\
Virginia Polytechnic Institute and State University \\
in partial fulfillment of the requirements for the degree of

\vfill

Master of Science \\
in \\
Computer Science and Application

\vfill

Binoy Ravindran, Chair \\
Ali R. Butt Co-Chair \\
Dongyoon Lee

\vfill

June 17, 2016 \\
Blacksburg, Virginia

\vfill

Keywords: State Machine Replication, Runtime Systems, Deterministic System, System Software
\\
Copyright 2016, Yuzhong Wen

\end{center}

\pagebreak

\thispagestyle{empty}
\begin{center}

{\large Replication of Concurrent Applications in a Shared Memory Multikernel}

\vfill

Yuzhong Wen

\vfill

(ABSTRACT)

\vfill

\end{center}
%Modern software systems are becoming complicated than ever before. 
State Machine Replication (SMR) has become the de-facto methodology of building a fault-tolerance system. Current SMR systems usually have multiple machines involved, each of the machines in the SMR system acts as the replica of others. However having multiple machines leads to more cost to the infrastructure, in both hardware cost and power consumption. For tolerating non-critical CPU and memory failure that won't crash the entire machine, there is no need to have extra machines to do the job. As a result, intra-machine replication is a good fit for this scenario. However, current intra-machine replication approaches do not provide strong isolation among the replicas, which allows the faults to be propagated from one replica to another. 

In order to provide an intra-machine replication technique with strong isolation, in this thesis we present a SMR system on a multi-kernel OS. We implemented a replication system that is capable of replicating concurrent applications on different kernel instances of a multi-kernel OS. Modern concurrent application can be deployed on our system with minimal code modification. Additionally, our system provides two different replication modes that allows the user to switch freely according to the application type.

With the evaluation of multiple real world applications, we show that those applications can be easily deployed on our system with 0 to 60 lines of code changes to the source code. From the performance perspective, our system only introduces 0.23\% to 63.39\% overhead compare to non-replicated execution. With the low overhead and transparency to the application, our system has reached the standard of being used in production.

\vfill

% GRANT INFORMATION

This work is supported by AFOSR under the grant FA9550-14-1-0163.  Any opinions, findings, and conclusions expressed in this thesis are those of the author and do not necessarily reflect the views of AFOSR.

\pagebreak

% Dedication and Acknowledgments are both optional
% \chapter*{Dedication}
\chapter*{Acknowledgments}


\tableofcontents
\pagebreak

\listoffigures
\pagebreak

\listoftables
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}

\newcommand{\detstart}{\_\_det\_start}
\newcommand{\detend}{\_\_det\_end}
\newcommand{\dettick}{\_\_det\_tick}

\input{introduction}
\input{popcornlinux}
\input{logicaltimedet}
\input{schedrep}
\input{runtime}
\input{evaluation}
\input{conclusion}


\bibliographystyle{unsrt}
\bibliography{bibliography}
%\input{tla/Det}
\end{document}

